---
title: "The Office"
author: "Your NAME"
output: github_document
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(tidymodels)
library(schrute)
library(lubridate)
```

## Overview
The goal of this exercise is to predict IMDB scores for episodes of The Office using the `theoffice` dataset from the [**schrute**](https://bradlindblad.github.io/schrute/) package. This exercise will guide you through the steps of feature engineering, model building, cross-validation, and performance comparison.

### Learning Objectives
1. Practice feature engineering using text data.
2. Develop a linear regression model and preprocess data with recipes.
3. Perform cross-validation and interpret model metrics.
4. Compare model performance and make predictions.

## Dataset Description

The `theoffice` dataset contains information about episodes of *The Office*, including:
- **imdb_rating**: IMDB rating for the episode (target variable).
- **season** and **episode**: Identifiers for episodes.
- **air_date**: Date the episode aired.
- **total_votes**: Total votes the episode received on IMDB.
- **character lines**: Lines spoken by each character (stored as text).
- **scripts**: Transcripts of episodes.

### Step 1: Examine the Data
Start by examining the structure of the `theoffice` dataset.


```{r}
glimpse(theoffice)
```
### Step 2: Preprocessing Air Date

The `air_date` column is stored as a character and needs to be converted into a Date format for later use.

```{r}
theoffice <- theoffice %>%
  mutate(air_date = ymd(as.character(air_date)))
```

### Step 3: Verify Unique Episodes
Check the distinct combinations of season and episode in the dataset:

```{r}
theoffice %>%
  distinct(season, episode)
```

## Exercises 

### Exercise 1 - Calculate the Percentage of Lines Spoken by Key Characters

For each episode, calculate the percentage of lines spoken by Jim, Pam, Michael, and Dwight. This requires:
- Grouping the data by `season` and `episode`.
- Summing the total lines for each character and calculating their percentage.

**Hint**: Use `str_detect()` to identify lines spoken by each character and calculate their count.

Expected Output (example structure):

| season | episode | character | percentage_lines |
|--------|---------|-----------|------------------|
| 1      | 1       | Jim       | 20%             |


```{r lines}

```

### Exercise 2 - Identify Episodes for Special Occasions

Identify episodes that touch on Halloween, Valentine's Day, and Christmas. Look for keywords in the episode scripts.

**Hint**:
- Use `str_detect()` on the `scripts` column.
- Search for keywords like "Halloween," "Valentine," "Christmas."

Expected Output (example structure):

| season | episode | occasion       |
|--------|---------|----------------|
| 2      | 5       | Halloween      |
| 3      | 10      | Christmas      |

```{r special-episodes}

```

### Exercise 3  - Create a Modeling Dataset

Engineer features based on episode scripts and create a modeling dataset. Add an indicator variable `michael`:
- `michael = 1` if Michael Scott (Steve Carrell) appears in the episode.
- `michael = 0` if Michael Scott does not appear.

**Hint**: Michael Scott left the show at the end of Season 7.

Expected Output (example structure):

| season | episode | feature_1 | feature_2 | michael |
|--------|---------|-----------|-----------|---------|

```{r office-df}

```

### Exercise 4 - Split the Data

Split the dataset into training (75%) and testing (25%).

**Hint**: Use `initial_split()` from the `rsample` package.

```{r split}
set.seed(1122)

```

### Exercise 5 - Specify a Linear Regression Model

Specify a linear regression model for predicting `imdb_rating`.

```{r model}

```

### Exercise 6 - Create a Recipe

Develop a preprocessing recipe:
1. Update the role of `episode_name` to not be a predictor.
2. Remove `air_date` as a predictor.
3. Treat `season` as a factor.
4. Remove all zero variance predictors.

**Hint**: Use `step_rm()` and `step_zv()` for removal steps.

```{r recipe}

```

### Exercise 7 - Build a Workflow

Build a workflow for fitting the model specified earlier and using the recipe you developed to preprocess the data.

```{r workflow}

```

#### Exercise 8 - Fit the Model and Interpret Coefficients

Fit the model to the training data and interpret the slope coefficients for at least two predictors.

**Hint**: Use `tidy()` to extract coefficients after fitting the model.

```{r fit}

```

### Exercise 9 - Perform Cross-Validation

Perform 5-fold cross-validation to evaluate the model. Report performance metrics like RMSE.

**Hint**:
- Use `vfold_cv()` to create folds.
- Fit the model using `fit_resamples()`.


```{r cv, message=FALSE, error = TRUE}
set.seed(345)
folds <- vfold_cv(___, v = ___)
folds

set.seed(456)
office_fit_rs <- ___ %>%
  ___(___)

___(office_fit_rs)
```

### Exercise 10 - Compare Models on Testing Data

Use your model to make predictions for the testing data and calculate the RMSE. 
Use the old model (provided below) to make predictions and calculate RMSE.
Which model did a better job in predicting IMDB scores for the testing data?Compare the two models to determine which performs better.

**Hint**: Use `yardstick` metrics like `rmse()` for comparisons.

#### New model

```{r new-model}

```

#### Old model

```{r old-model, error = TRUE}
office_mod_old <- linear_reg() %>%
  set_engine("lm")

office_rec_old <- recipe(imdb_rating ~ season + episode + total_votes + air_date, data = office_train) %>%
  # extract month of air_date
  step_date(air_date, features = "month") %>%
  step_rm(air_date) %>%
  # make dummy variables of month 
  step_dummy(contains("month")) %>%
  # remove zero variance predictors
  step_zv(all_predictors())

office_wflow_old <- workflow() %>%
  add_model(office_mod_old) %>%
  add_recipe(office_rec_old)

office_fit_old <- office_wflow_old %>%
  fit(data = office_train)

tidy(office_fit_old)

___
```
